Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery.

### 2024-03-01 docs/_tex/index.tex
Pierre comments

\subsection{\texorpdfstring{\textbf{Spectral Spatial Temporal Resolution
impact on the
prediction}}{Spectral Spatial Temporal Resolution impact on the prediction}}\label{spectral-spatial-temporal-resolution-impact-on-the-prediction}

@@

>>>>

\subsection{Spectral Spatial Temporal Resolution impact on the
prediction}\label{spectral-spatial-temporal-resolution-impact-on-the-prediction}

@@

In the present study, the main novelty is the usage of two different
altitude (12m and 120m) in the neural network model building. The
spatial resolution of the low altitude fights (8mm) allows for an
accurate selection of pure pixel of the classes used in the neural
network model

### 2024-03-01 index.qmd
Pierre comments

## **Spectral Spatial Temporal Resolution impact on the prediction**

@@

```{r Plot Reflectance_Validation 2 height}
#| cache: false
#| echo: false
#| warning: false
#| fig-cap: Comparison of reflectance retrieved from both low-altitude and high-altitude flights over a common area. The red dashed line represents a 1 to 1 relationship. 
#| label: fig-CompareRef
#| fig-width: 5
#| fig-height: 5
#| out-width: "50%"

@@

knitr::include_graphics("./Figures/Compare_reflectance.png")
```

>>>>

## Spectral Spatial Temporal Resolution impact on the prediction

@@

::: columns
::: column
```{r Plot Reflectance_Validation 2 height}
#| cache: false
#| echo: false
#| warning: false
#| fig-cap: Comparison of reflectance retrieved from both low-altitude and high-altitude flights over a common area. The red dashed line represents a 1 to 1 relationship. 
#| label: fig-CompareRef
#| fig-width: 5
#| fig-height: 5
#| out-width: "50%"

@@

knitr::include_graphics("./Figures/Compare_reflectance.png")
```
:::

::: column
In the present study, the main novelty is the usage of two different altitude (12m and 120m) in the neural network model building. The spatial resolution of the low altitude fights (8mm) allows for an accurate selection of pure pixel of the classes used in the neural network model
:::
:::
